### 2014-10-31 fundamentals/qa.tex
mostly including gls

Cyclus acknowledges that quality assurance is an on-going process throughout the 
entire life of the code. As a simulator where most modeling decisions are made 
by third party archetype developers or users, the most important feature of QA 
is verification. Validation may be impossible and \gls{UQ} is beyond the scope.

@@

Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software 
development components that comprise the \Cyclus verification strategy.
Each of these on its own is a valuable addition to QA but is cannot be the 
entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly 
adhered to they present a fortress through which undesirable code may siege, 
but never take.

@@

Automated software \emph{testing} is the first line of defense against
errors in implementation. It also acts as an early warning sign that the
simulator does or does not work as intended on a new system.
Testing serves a critical role in QA because it directly compares the 
results of running software versus the expected behavior of the software.
In \Cyclus, three categories of tests are defined: unit tests, integration 
tests, and regression tests.

@@

All of the public interface (the \gls{API}) must be documented as part of \Cyclus
QA policy. This certifies that the intention for a code unit is communicated 
in way that is separate from its implementation. This policy is important 
because implementations are often wrong, hence bugs. They are thus unreliable 
resources about themselves. Truly trustworthy communication about what 
software should be doing comes from the author explicitly stating the 
goals of an \gls{API} in prose form. Future development of the code is then able to 
compare the implementation versus the documentation to discern whether or not they 
are in agreement. Documentation is thus a secondary higher-level information 
stream.  In \Cyclus, this information is aggregated together into static 
websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx 
\cite{brandl_sphinx_2014} 
tools. These websites are placed online at \url{http://fuelcycle.org}.

@@

CI has become a necessary but not sufficient addition to the \Cyclus QA
system. Its merit is that it keeps bad code out. However, \Cyclus will always
require human eyes and human hands to let good code in.

>>>>

\Cyclus acknowledges that quality assurance is an on-going process throughout the 
entire life of the code. As a simulator where most modeling decisions are made 
by third party archetype developers or users, the most important feature of 
\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond 
he scope.

@@

Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software 
development components that comprise the \Cyclus verification strategy.
Each of these on its own is a valuable addition to \gls{QA} but is cannot be the 
entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly 
adhered to they present a fortress through which undesirable code may siege, 
but never take.

@@

Automated software \emph{testing} is the first line of defense against
errors in implementation. It also acts as an early warning sign that the
simulator does or does not work as intended on a new system.
Testing serves a critical role in \gls{QA} because it directly compares the 
results of running software versus the expected behavior of the software.
In \Cyclus, three categories of tests are defined: unit tests, integration 
tests, and regression tests.

@@

All of the public interface (the \gls{API}) must be documented as part of \Cyclus
\gls{QA} policy. This certifies that the intention for a code unit is communicated 
in way that is separate from its implementation. This policy is important 
because implementations are often wrong, hence bugs. They are thus unreliable 
resources about themselves. Truly trustworthy communication about what 
software should be doing comes from the author explicitly stating the 
goals of an \gls{API} in prose form. Future development of the code is then able to 
compare the implementation versus the documentation to discern whether or not they 
are in agreement. Documentation is thus a secondary higher-level information 
stream.  In \Cyclus, this information is aggregated together into static 
websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx 
\cite{brandl_sphinx_2014} 
tools. These websites are placed online at \url{http://fuelcycle.org}.

@@

CI has become a necessary but not sufficient addition to the \Cyclus \gls{QA}
system. Its merit is that it keeps bad code out. However, \Cyclus will always
require human eyes and human hands to let good code in.
